\section{Hardware Framework}
\label{sec:hardwareframework}

\subsection{Purpose}
The hardware framework allows different chips to be utilized with the same software code the same generated code from our software package ``PLCEdit'' as described in chapter \ref{ch:software}. Provided the hardware meets the minimum requirements defined by section \ref{sec:hardwareplatform}. The framework consists of a bunch of definitions which map the symbolic software references to hardware specific points. In addition the framework is also responsible for properly initializing the chip and performing any clean up operations once the chip finishes execution.


\subsection{Hardware Framework Overview}
TODO: include a diagram of the different hardware sections and how they fit together including the userland program.


TODO: Describe each section in detail.


\subsection{Chip Initialization} 
\textbf{File:} plcmcu.h

\textbf{Section:} Chip configuration 

\textbf{Description:} Sets configuration bits for the chip that cannot be done at runtime.

\textbf{Code:}
\\
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}[frame=single]
...
#pragma config OSC = HSPLL //set occilator to HS-PLL
#pragma config OSCS = OFF //disable occilator switch
#pragma config PWRT = OFF //enable power on timer
#pragma config WDT = OFF //disable watchdog timer
#pragma config LVP = OFF //disable low power programming
...
\end{lstlisting}
\end{minipage}
\\
\\
\textbf{File:} plcmcu.c

\textbf{Routine:} init\_chip(void)

\textbf{Description:} Initializes any chip specific configuration bits that must be done at runtime.

\textbf{Code:}
\\
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}[frame=single]
...
void init_chip(void)
{	
	TRISA = 0xFF; //set all portA to input
	TRISB = 0x00; //set all portB to output
}
...
\end{lstlisting}
\end{minipage}
\\
\\
\subsection{Hardware Specific Definitions}

Hardware specific definitions are reserved for defining specific characterists of the hardware to match up with the software. For example it may be necessary to define the input and output ports to a specific port on the chip itself.
\\
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}[frame=single]
...
/* PORT specification */
#define PORTOUT PORTB
#define PORTIN PORTA
...
\end{lstlisting}
\end{minipage}
\\
\\
\subsection{Hardware Specific Implementations}

convenience calls from our software that access more complex operations may be required to be implimented directly into hardware. Our current software only requires that the routine for delaying the execution by a number of milliseconds is implimented. It is done as follows:

\textbf{File:}plcmcu.h
\\
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}[frame=single]
/* CLOCK specification */
...

#define OCCILATOR 10000000 //our occilator in seconds
#define TCYTIME 1 //now many cycles / instruction 4 for non PLL 1 for PLL 

#define TCYTICK OCCILATOR / TCYTIME //how long per instruction tick
#define MSTIME 1000 //milliseconds to seconds

#define MSTCY TCYTICK / MSTIME //how many clocks in a ms (10000 for pll)

//crystal select block
#if (MSTCY >= 10000)
	#define DEFDELAY(timevalms) Delay10KTCYx(timevalms * (char) (MSTCY/10000))
#endif
#if (MSTCY >= 1000 && MSTCY void delayms(int time)
{
	DEFDELAY(time);
}< 10000)
	#define DEFDELAY(timevalms) Delay1KTCYx(timevalms * (char) (MSTCY/1000))
#endif
#if (MSTCY < 1000)
	#error "Unsupported OCCILATOR defined by hardware manufacturer please ensure crystal is faster than 1Mhz"
#endif

/* End CLOCK specification */

...
\end{lstlisting}
\end{minipage}
\\
\\
\textbf{File:} plcmcu.c
\\
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}[frame=single]
...
void delayms(int time)
{
	DEFDELAY(time);
}
...
\end{lstlisting}
\end{minipage}
\\
\\
It is highly recommended to avoid macros where possible however the nature of the PIC18F452 required macros in order to prevent inaccurate delays caused by actually computations.