\section{Platform}
\label{sec:hardwareplatform}

In Ladder Logic the compiled code runs on an embedded microcontroller in the PLC\glossary{name={PLC},description={Programmable Logic Controller}}. Similarily for \plccharts we also require such a hardware platform to run our generated code (see Section~\ref{sec:implementation:struct}). The initial hardware platform chosen for this project was the PIC18F452 however this project was designed from the ground up to allow for other hardware to be untilized with some effort from a hardware support team. The PIC18F452 was chosen for this project due to its popularity in the industry and low cost.

In addition the PIC18F452 has the following features that are essential 
for PLC construction:

\begin{itemize}
\item 8 Digital inputs.
\item 8 Digital outputs.
\item 2 Ports.
\item Has support for C syntax.
\item Accessible hardware clock.
\item On board program memory.
\end{itemize}

These minimum specification have become the baseline for our hardware 
requirements. In order to utilize a different chip with our programming 
software the hardware support team will be required to implement a framework 
layer as described in Section \ref{sec:hardwareframework}.

For real time operation hardware requirements on clock speed will 
become more critical execution of ``goto'' should occur as close as
 possible to constant time or O(1). Without the ability to execute 
 ``goto'' in constant time delays between transitions become 
 increasingly harder to predict and account for.

The specifications for the PIC18F452 are as follows:
\begin{itemize}
	\item CPU Frequency: 40Mhz
	\item Program Memory: 32K
	\item Data Memory: 1536 Bytes
	\item I/O Ports: 5
	\item Timers: 4
	\item 10-Bit A/D: 8 inputs channels
\end{itemize}

As the reader may observe the PIC18F452 exceeds our minimum 
requirements for hardware that will run our OS and software. In 
particular we currently do not include provisions to take inputs 
from our A/D channels. This was done because the original design had 
separate I/O modules to handle the inputs and outputs. Given more 
time on this project it would have been possible to more fully utilize 
the on board hardware.
